---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tmsamples

<!-- badges: start -->
<!-- badges: end -->

The goal of tmsamples is to simulate term frequency matrices (DTMs or TCMs) based
on parameters from real or simulated probabilistic topic models. 

This corpus simulation is a core part of my dissertation research. The basic
idea is: if you can simulate a corpus using the functional form of a topic model,
and that corpus retains the gross statistical properties of human language, then
we can use simulated corpora to derive rules and metrics to fit well specified
topic models. Conversely, we can avoid pathologically misspecified models.

## Installation

You can install the GitHub version of tmsamples with:

``` r
library(remotes)
remotes::install_github("tommyjones/tmsamples")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tmsamples)


Nk <- 4
Nd <- 50
Nv <- 1000

alpha <- rgamma(Nk, 0.5)

beta <- generate_zipf(vocab_size = Nv, magnitude = 500, zipf_par = 1.1)

pars <- sample_parameters(alpha, beta, Nd)

doc_lengths <- rpois(Nd, 50)

dtm <- sample_documents(
  theta = pars$theta,
  phi = pars$phi,
  doc_lengths = doc_lengths,
  threads = 2 ## threads controls parallel computation
)



```


